How to be a good member of a scientific software community [Article v\versionnumber]

### 2021-08-16 paper.tex
more text
lots more text

The second step is to check the manual. This might seem trivially obvious, but
you'd be astonished how many emails developers get that are directly answered in
the manual. If the manual is short, you can read the whole thing. If it's
longer, search for relevant-seeming keywords, scan the sections that seem to
pertain to your error message. If there's an FAQ (frequently asked questions)
list, check that first.

@@

Finally, you can consider diving into the code. This decision depends very much
on the complexity of the package, your skill level, and how urgently you need
the solution. More often than not, comprehending the whole software package will
be too time consuming, but there are tricks and shortcuts one can use to at
least figure out where things might be going wrong. Figuring out where the error
is occurring can sometimes help you figure out why it happened, so examine the
stack trace if there is one. Alternatively, you can search the code base for the
error message, to see what drove the error; it's not uncommon for the comments
in the code to be clearer and more indicative of what could go wrong than the
error message itself. To be clear: as an end user, \emph{you are not obligated
to check the code}, but it can sometimes be a good shortcut to help you either
solve your problem on your own or give the developers what they need to solve
it. Moreover, if you do solve the problem, it's a good idea to share your
solution with the developers; most will be grateful to you for your help.

@@

@@

For a feature request, you would also describe what you hope to accomplish and
how you'd like to see it work, as well as any current workaround you've
developed.

@@

This should go without saying, but if you're asking for help it behooves you to
do so respectfully. We're not saying that you need to be obsequious. Rather,
approach every interaction with respect: respect for people's time, respect for
their ideas, respect for their identity. If you're asking for help, do so with
the perspective that the developer is volunteering their time to help you, with
minimal payoff to them.  If you're reporting a bug, you're almost certainly
frustrated; try not to take that frustration out on the developers. If you're
offering a new feature, keep in mind that it may not align with the developers'
vision for where the software is going.

@@

This paper has focused on what software consumers should do when asking for
help.  However, this does not mean that the developers of scientific software
are without responsibilities. If we want users to behave in a certain way, it
behooves us to tell them that. Users approaching us in good faith deserve to be
treated fairly and courteously.

@@

@@

% We suggest you preserve this comment:
For a more detailed description of contributions from the community and others, see the GitHub issue tracking and changelog at \githubrepository.

@@

\section{Funding Information}
%%%%%%%
% Authors should acknowledge funding sources here. Reference specific grants.
%%%%%%%
This work supported in part by NIH R21GM138970 to AG.

>>>>

The second step is to check the manual. This might seem trivially obvious, but
you'd be astonished how many emails developers get that are directly answered in
the manual. If the manual is short, you can read the whole thing. If it's
longer, search for relevant-seeming keywords, scan the sections that seem to
pertain to your error message. If there's an FAQ (frequently asked questions)
list, check that first; asking an FAQ is likely to lead to grumbling.

@@

Finally, you can consider diving into the code. This decision depends very much
on the complexity of the package, your skill level, and how urgently you need
the solution. More often than not, comprehending the whole software package will
be too time consuming, but there are tricks and shortcuts one can use to at
least figure out where things might be going wrong. Figuring out where the error
is occurring can sometimes help you figure out why it happened, so examine the
stack trace if there is one. Alternatively, you can search the code base for the
error message, to see what drove the error; it's not uncommon for the comments
in the code to be clearer and more indicative of what could go wrong than the
error message itself. To be clear: as an end user, \emph{you are not obligated
to check the code}, but it can sometimes be a good shortcut to help you either
solve your problem on your own or give the developers what they need to solve
it. Moreover, if you do solve the problem, it's a good idea to share your
solution with the developers; most will be grateful to you for your help, and
they have comments or improvements suggested improvements. If the package is
hosted on GitHub, consider opening a pull request so your solution can be merged
into the main branch.

@@

    \item Give the version of the code you're using.

@@

Sometimes, the developer will be able to answer your question based on the first
email. However, their reply will often contain questions or suggestions for
things to test. \emph{It is crucial that you read this message carefully, and
answer all of the questions to the best of your ability when you reply.} As a
rule, these questions aren't asked idly; the person providing support is trying
to help you! Far too often, users don't read the reply email carefully, don't
answer the questions, try only the first suggestion, or refuse to indicate what
it is they were actually doing. If you do this, the best case is that it will
take longer for you to get to a solution. More likely, you will frustrate the
person trying to help you, and they may become reluctant to work on your issue.

Feature requests are similar: you need to describe what you hope to accomplish
and how you'd like to see it work, as well as any current workaround you've
developed. Keep in mind that many features sound easy, but there can be deep
design issues that make their implementation difficult. Moreover, it is possible
that the developer won't be enthusiastic about your idea, even if it is doable
--- for example, it might not coincide with their vision for the software. Or,
as discussed above, academic developers are generally not compensated for their
work (obtaining NIH funds to support software development is extremely
difficult) and simply might not have the time to work on new features.

@@

This should go without saying, but if you're asking for help it behooves you to
do so respectfully. We're not saying that you need to be obsequious. Rather,
approach every interaction with respect: respect for people's time, respect for
their ideas, respect for their identity (including among other things race,
ethnicity, country, sex or gender, or career stage). If you're asking for help,
do so with the perspective that the developer is volunteering their time to help
you, with minimal payoff to them.  If you're reporting a bug, you're almost
certainly frustrated; try not to take that frustration out on the developers. If
you're offering a new feature, keep in mind that it may not align with the
developers' vision for where the software is going.

@@

This paper has focused on what software consumers should do when asking for
help.  I suppose it could even be read as a list of complaints about bad
behavior by users (though that's not how I intend it). However, each behavior
described above has a corresponding expectation for the developers.

However, this does not mean that the developers of scientific
software are without responsibilities. If we want users to behave in a certain
way, it behooves us to tell them that. Users approaching us in good faith
deserve to be treated fairly and courteously.

@@

Moreover, it's not enough for you as a developer to treat people with respect.
To the extent that there's a community around your software, you must attempt to
make sure that community is respectful; as developer, your words and deeds carry
significant weight. If you call out bad behavior (or even marginal behavior),
that will go a long way towards setting a good tone for your community. If you
let it slide, chances are others will assume you implicitly endorse it.

@@

% We suggest you preserve this comment:
For a more detailed description of contributions from the community and others, see the GitHub issue tracking and Changelog at \githubrepository.

@@

\section{Funding Information}
%%%%%%%
% Authors should acknowledge funding sources here. Reference specific grants.
%%%%%%%
This work supported in part by NIH R21GM138970 to Alan Grossfield.
